Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality

### 2024-09-10 paper/ms.tex
Update based on image rhalf change

In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts. In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$. Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square. All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used. Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$).

>>>>

In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts. In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$. Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square. All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used. Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$), and only resolution elements within 10 times the stellar half-mass radius of the center of the subhalo are used.
